Proposal: DINO Methods for Style Transfer

### 2022-03-04 Proposal.tex
so much tex setup

%%% Packeges %%%
\usepackage[margin=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{scrextend}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[noend]{algpseudocode}
\usepackage{bm}
% \usepackage{pythonhighlight}

%%% Links %%%
\hypersetup{
    colorlinks=true,     
    urlcolor=blue,
}

%%% Formatting %%%
\setlength{\headheight}{25pt}
\pagestyle{fancy}
\lhead{Sacha Goldman, Shirley Wang, Yuchong Zhang} 
\rhead{CSC413 Project Proposal}
\setlength{\parskip}{1em}
% \setlength\parindent{0pt}

%%% Commands %%%
\newcommand{\powerset}{\mathcal P}
\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\Q}{\mathbb Q}
\newcommand{\Z}{\mathbb Z}
\newcommand{\N}{\mathbb N}
\newcommand{\E}{\mathbb E}
\renewcommand{\P}{\mathbb P}
\renewcommand{\Re}{\text{Re }}
\renewcommand{\Im}{\text{Im }}
\newcommand{\der}[2]{\frac{d #1}{d #2}}
\newcommand{\pder}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\iso}{\cong}
\newcommand{\divs}{\big\vert}
\newcommand{\boundry}{\partial}
\newcommand{\cross}{\times}
\newcommand\lit[1]{{\texttt{"#1"}}}
\newcommand{\norm}[1]{\left| \left| #1 \right| \right|}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}
\newcommand{\lemma}[2]{\textbf{Lemma} \begin{indented} #1 \end{indented} \textbf{Proof of Lemma} \begin{indented} #2 \end{indented}}
\newcommand{\induction}[2]{\textbf{Base Case} \begin{indented} #1 \end{indented} \textbf{Inductive Case} \begin{indented} #2 \end{indented}}
\newcommand{\note}[1]{\textbf{Note:} #1}
\renewcommand{\phi}{\varphi}
\newcommand{\err}[1]{\overline{#1}}
\newcommand{\tr}{\text{trace}}

%%% Enviroments %%%
\newenvironment{pseudo}{\begin{algorithmic}[1]}{\end{algorithmic}}
\newenvironment{indented}[1][1.5]{\begin{addmargin}{#1em}}{\end{addmargin}}

%%% Document %%%
\begin{document}
\end{document}

>>>>

\PassOptionsToPackage{numbers, compress}{natbib}

\usepackage[final]{proposal_neurips_2021}

\bibliographystyle{abbrvnat}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}

\title{Proposal: DINO Methods for Style Transfer}

\author{
  Sacha Goldman \\
  Department of Computer Science\\ 
  Department of Mathematics\\
  University of Toronto\\
  Toronto, ON M5S 1A1 \\
  \texttt{sacha.goldman@mail.utoronto.ca} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Related Works}

\section{Method}

\medskip

% Our current sources
\nocite{*}

\bibliography{bib}

\end{document}
